Filling in data gaps on refugee children: Statistical imputation for missing count data

### 2023-01-09 paper.qmd
predictive checks

p.imputations.syr.children <- ggplot(data = imputations.syr %>% filter(asylum_iso3 %in% c("SWE", "USA",  "MCO",  "LBN", "JOR", "GBR")),
      aes(y=reorder(asylum_country, childrenProp), x=childrenProp)) +
     stat_halfeye()

>>>>

p.imputations.syr.children <- ggplot(data = imputations.syr %>% filter(asylum_iso3 %in% c("SWE", "USA",  "MCO",  "LBN", "JOR", "GBR")),
      aes(y=reorder(asylum_country, childrenProp), x=childrenProp)) +
     stat_halfeye() +
  theme_minimal()
